\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Yan Li} % Your name
\address{1990~$\cdot$~09 \\ Rd. Zhiwei, District Pudong East, Shanghai, China}
\address{(+86)~$\cdot$~185~$\cdot$~2100~$\cdot$~2247 \\ iSeaSoul@gmail.com}

\begin{document}

\begin{rSection}{EDUCATION}

{\bf Wuhan University} \hfill {\em September 2011 - June 2013} \\
Master in Computer Software \& Theory
\vspace{0.3em}

{\bf Wuhan University} \hfill {\em September 2007 - June 2011} \\
B.S. in Computer Science \& Technology
\vspace{0.5em}

\end{rSection}

\begin{rSection}{EXPERIENCE}

\begin{rSubsection}{Baidu Ecom}{November 2014 - Present}{Senior RD}{Shanghai, China}
\item Develop new features in "Shantou" project group.
\item Participate in the algorithm optimization of Click Through Rate(CTR) prediction for Baidu Advertise search engine.
\item Participate in the "Realtime Learning" project, reduce the time of extracting training instance from 3 hours to 10 minutes, use PU learning algorithm to reduce the influence of the false instances, and improve AUC of the online DNN model by 0.2-0.3 percent points (C++ / Python).
\end{rSubsection}

\begin{rSubsection}{NetEase Game}{July 2013 - July 2014}{Senior Development Engineer}{Hangzhou, China}
\item Finish a small but whole card mobile game in the training project within 2 months. Be responsible for all framework and logic in server-end.
\item Participate in the development of a new mobile game, as one of the two primal program developers for this project, complete the core work including game engine, database design, client architecture and logging system in collaboration (C++ / Python / JavaScript).

\end{rSubsection}
\begin{rSubsection}{Microsoft STC}{February 2012 - June 2012}{SDET Intern}{Beijing, China}
\item Participate in building a complete training platform using ASP.NET MVC 3.0, to train a new extraction model for News webpages in Bing Search, and the PR value of the new model had been much-improved.
\item Some data analysis and mining work (C\#).
\end{rSubsection}

\end{rSection}

\begin{rSection}{HONORS}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.2em \vspace{0em}
\item Google Code Jam (GCJ) 2014~~Onsite Round (Top 25 worldwide)  \hfill {2014}
\item The $36^{th}$ ACM-ICPC World Finals~~Rank $18^{th}$  \hfill {2012}
\item The $35^{th}$ ACM-ICPC World Finals~~Rank $42^{nd}$  \hfill {2011}
\item The $34^{th}$ - $36^{th}$ ACM-ICPC Asia Regionals~~8 Gold, 2 Silver \hfill {2009 - 2011}
\item The $1^{st}$ "Tao of Jisuan" Programming Contest~~Onsite Round \hfill {2015}
\item The $2^{rd}$ Microsoft "Beauty of Programming" Challenge Competition~~Onsite Round \hfill {2013}
\item Tencent Hackathon 2012~~Second Place \hfill {2012}
\item Central China mathematical modeling Invitational Competition~~First Prize \hfill {2009}
\item Microsoft Intern "SanGuoSha" 3V3 Game Competition~~First Place \hfill {2012}  % Just kidding
\item Wuhan University "2011 Excellent Graduates"~~Honor Title \hfill {2011}
\end{list}
\vspace{0.5em}

\end{rSection}

\begin{rSection}{TECHNICAL STRENGTHS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, C\#, Python, Java, JavaScript, Scheme, Scala, Shell, \LaTeX \\
Tools & SVN, Git, Vim, Sublime\\
English & CET-4, CET-6 \\
Others & Algorithm, Machine Learning, Parallel Programming
\end{tabular}

\end{rSection}

\end{document}
